A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-05 latex/main.tex
Updates from Overleaf

In the ARG, XR, XU, XAA, XAG, and XAM
are nested under the XQ recombinant lineage.
These lineages were designated around the same time,
roughly within a five-month period (Mar. to Jul., 2022).
Also, their breakpoint intervals of these lineages,
as suggested in the Pango designation issues,
all occur at the 5' end of the genome
within a $\sim$5,000 base segment ($\sim$4,300 to $\sim$9,400).

>>>>

In the ARG, XR, XU, XAA, XAG, and XAM
are nested under the XQ recombinant lineage.
These lineages were designated around the same time,
approximately within a five-month period (Mar. to Jul., 2022).
The breakpoint intervals of these lineages,
as suggested in the Pango designation issues,
all occur at the 5' end of the genome,
within a $\sim$5 kb segment ($\sim$4,300 to $\sim$9,400):
% TODO: Add URLs to Pango issues?
XQ (4321-5387), % https://github.com/cov-lineages/pango-designation/issues/468
XAG (6515-8394), % https://github.com/cov-lineages/pango-designation/issues/709
XU (6517-9345), % https://github.com/cov-lineages/pango-designation/issues/522
XAM (8087-9193), % https://github.com/cov-lineages/pango-designation/issues/759
and XAA (8392-9345). % https://github.com/cov-lineages/pango-designation/issues/664
